Forecasting the 2024 US General Election

### 2024-11-03 paper/paper.qmd

Lorem Ipsum

>>>>

The pollster that is chosen to be analyzed is The New York Times/Siena College. The population targeted by this poll consists of the entire U.S. electorate. The frame for the poll is derived from the L2 voter file, which is a nonpartisan database, and further supplemented by matched cellular telephone numbers from Marketing Systems Group (The New York Times, 2024). From this frame, respondents are randomly selected from a national list of registered voters to participated in telephone interviews in English and Spanish (The New York Times, 2024). To enhance its regional and demographic representativeness, the national poll includes separate samples for Florida (622 voters) and Texas (617 voters) and applies oversampling to ensure adequate responses from key demographic groups, specifically Black voters and Hispanic voters (The New York Times, 2024). The poll’s oversample includes 589 Black voters and 902 Hispanic voters, with subcategories for individuals identifying as a single or multiple races or ethnicities (The New York Times, 2024). By adjusting the weights of these subgroups in the final analysis, the poll aims to produce results reflective of the national electorate (The New York Times, 2024).

The sample for this poll was recruited through a stratified sampling method, which considered factors such as state, party affiliation, race, gender, and age (The New York Times, 2024). Each stratum was adjusted to address differential coverage and expected response rates, with the initial selection weights reflecting the reciprocal of a stratum’s telephone coverage and modeled response rate based on historical nonresponse data from prior polls (The New York Times, 2024). The poll’s stratification process included additional adjustments by state to accommodate varying levels of telephone number productivity (The New York Times, 2024). The sampling approach allows for representation of diverse demographics and achieves a more balanced sample, but it introduces trade-offs. While oversampling minority groups improves representation and allows for deeper analysis, the increased sampling error for these smaller subgroups complicates the interpretation of subgroup findings relative to the broader electorate (The New York Times, 2024).

Nonresponse is managed through stratified sampling adjustments, where mean response rates for each stratum help inform weighting to minimize potential bias from nonresponse (The New York Times, 2024). Additionally, the survey package in R is used to apply a series of weights, which adjusts the data based on various demographic characteristics and compensates for nonresponse at both the sample and question level (The New York Times, 2024). For instance, demographic adjustments are made based on age, party affiliation, race, and educational attainment (The New York Times, 2024). Moreover, among respondents with multiple contact numbers, the poll selects the number with the highest predicted response rate, further mitigating nonresponse bias and increasing the likelihood of respondent participation (The New York Times, 2024).

The questionnaire used in The New York Times/Siena College poll has several strengths aimed at enhancing accuracy, representativeness, and reliability. One advantage lies in the survey's duration, with calls limited to less than 15 minutes to maintain respondent engagement (The New York Times, 2024). This approach helps reduce the likelihood of incomplete responses due to participant fatigue, thereby supporting data integrity. By incorporating a stratified sampling approach that oversamples in battleground states, the questionnaire captures opinions from critical regions likely to influence the presidential election outcome (The New York Times, 2024). This focus aligns with the Electoral College system, making the data more actionable for understanding the dynamics within these decisive states. Moreover, the reliance on voter registration files, which contain detailed demographic and geographic data for 200 million Americans, supports robust sample balancing and demographic matching. The voter file's information is used to ensure proportional representation across party lines, regions, race, age, and other critical attributes. This allows the questionnaire to better represent national diversity and enhances accuracy through weighting adjustments for underrepresented demographics, such as those without a college degree (The New York Times, 2024). The use of telephone interviews, despite declining response rates, remains one of the few methods to quickly access a randomized sample of voters. Alternative methods like email or mail recruitment introduce their own issues, such as attracting only highly interested individuals, potentially biasing the sample toward the politically active rather than the average voter (The New York Times, 2024). Furthermore, the poll's careful management of sampling error, with a +- 2.4-point margin for the national sample and +- 5 points for state polls, ensures a strong level of accuracy while acknowledging the inherent uncertainty in survey results.

Despite these advantages, the questionnaire also faces several limitations. As response rates have decreased in recent years, the representativeness of telephone surveys has likely suffered, as individuals are more reluctant to answer phone calls from unfamiliar numbers. This trend has increased the costs of conducting such surveys, as more calls are needed to reach a proportional sample, and some demographic groups may remain underrepresented despite weighting adjustments (The New York Times, 2024). The reliance on telephone interviews also risks excluding younger voters and others who rely primarily on digital communication, potentially skewing the data if not properly addressed through demographic balancing and weighting. Additionally, while the questionnaire's margin of error provides a statistical measure of confidence, this margin can be significant, particularly in close races where even a two-point margin could change interpretations and outcomes. This issue highlights the limitations of polling as a "blunt instrument" where minor fluctuations in results can feel disproportionately impactful in a close election context (The New York Times, 2024).
